---
title: "Visit Scotland Analysis"
output: html_notebook
---

## Setup

### Load Libraries

```{r}
library(tidyverse)
library(here)
library(sf)
library(infer)
library(ggridges)
library(modelr)
library(skimr)
```

### Run Cleaning Script, Read In Clean Data & Set Colour Scheme for Visualisations

```{r}
source(here("scripts/cleaning_script.R"))

regional_domestic_tourism_all <- read_csv(here("data/clean_data/regional_domestic_tourism_all_clean.csv"))
regional_domestic_tourism_individual <- read_csv(here("data/clean_data/regional_domestic_tourism_individual_clean.csv"))
regional_domestic_tourism_non_gb_clean <- read_csv(here("data/clean_data/regional_domestic_tourism_non_gb_clean.csv"))
international_visits <- read_csv(here("data/clean_data/international_visits_clean.csv"))
tourism_businesses <- read_csv(here("data/clean_data/tourism_businesses_clean.csv"))
dom_int_summary <- read_csv(here("data/clean_data/dom_int_summary_clean.csv"))
# international_visits_annual_summary <- read_csv(here("data/clean_data/international_visits_annual_summary_clean.csv"))
# domestic_annual <- read_csv(here("data/clean_data/domestic_annual_clean.csv"))

local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")

colour_scheme <- c("#540453", "#1d1d65", "#970061", "#b6cb2b", "#9fd6f3")
```

## Annual Average Stats

### Domestic

#### 5 Figure Summary

```{r}
dom_int_summary %>%
  filter(dom_int == "Domestic") %>% 
  skim()
```

```{r}
dom_int_summary %>%
  filter(dom_int == "International") %>% 
  skim()
```

#### IQR

```{r}
dom_int_summary %>%
  filter(dom_int == "Domestic") %>%  
  summarise(visits_iqr= IQR(visits),
            expenditure_iqr= IQR(spend))
```

```{r}
dom_int_summary %>%
  filter(dom_int == "International") %>%  
  summarise(visits_iqr= IQR(visits),
            expenditure_iqr= IQR(spend))
```

#### Median

```{r}
dom_int_summary %>%
  filter(dom_int == "Domestic") %>%  
  summarise(median_visits = median(visits),
            median_spend = median(spend))

```

```{r}
dom_int_summary %>%
  filter(dom_int == "International") %>%  
  summarise(median_visits = median(visits),
            median_spend = median(spend))
```

## Trends Over Time

### Over Time / Visits

```{r}

dom_int_summary %>% 
  ggplot() +
  geom_line(aes(x = year, y = visits, colour = dom_int),
          size = 2) +
  geom_point(aes(x = year, y = visits, colour = dom_int), 
             size = 4) +
  ylim(0, 15000) +
  labs(x = "\n Year",
       y = "Visitors (Thousands) \n",
       title = "Annual Visits",
       subtitle = "Domestic & International Overnight Vistors",
       colour = "") +
  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
  scale_colour_manual(values = c("Domestic" = "#540453",
                                 "International" = "#9fd6f3")) +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", 
                                  linetype = "dashed"))

```

### Over Time / Spend

```{r}

dom_int_summary %>% 
  ggplot() +
  geom_line(aes(x = year, y = spend, colour = dom_int),
          size = 2) +
  geom_point(aes(x = year, y = spend, colour = dom_int), 
             size = 4) +
  ylim(0, 4000) +
  labs(x = "\n Year",
       y = "Expenditure (Million GBP) \n",
       title = "Annual Expenditure",
       subtitle = "Domestic & International Overnight Vistors",
       colour = "") +
  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
  scale_colour_manual(values = c("Domestic" = "#540453",
                                 "International" = "#9fd6f3")) +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", 
                                  linetype = "dashed"))

```

## Domestic Tourism

#### Average Visits By Region

```{r}

regional_data_joined %>% 
  group_by(code) %>% 
  summarise(mean_visits = mean(visits)) %>% 
  ggplot(aes(fill = mean_visits)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Number of Domestic Vistors",
    subtitle = "By Region",
    fill = "Visits (Thousands)") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

```

#### Expenditure by Region

```{r}
regional_data_joined %>% 
  group_by(code) %>% 
  summarise(mean_exp = mean(expenditure)) %>% 
  ggplot(aes(fill = mean_exp)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Expenditure of Domestic Vistors",
    subtitle = "By Region",
    fill = "Expenditure (Million GBP)") +
    theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

#### Spend Per Visit

##### Mean Spend Per Visit Plot

```{r}
regional_domestic_tourism_individual %>%
  filter(visits != 0,
         expenditure != 0) %>% 
  mutate(exp_per_visit = expenditure / visits, rm.na = TRUE) %>%
  group_by(local_authority) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  arrange(desc(mean_exp_per_visit)) %>%
  ggplot() +
  geom_col(aes(x = reorder(local_authority, mean_exp_per_visit), y = mean_exp_per_visit,
               fill = local_authority %in% c("City of Edinburgh", "Glasgow City", "Highland")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey80",
                               "TRUE" = colour_scheme[1])) +
  coord_flip() +
  labs(
    x = "Region",
    y = "Mean Expenditure per Visit (Million GBP / Thousand Visits)",
    title = "Domestic Tourism Mean Expenditure per Visit") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "blank"))
```

#### Nights Stayed

##### Plot

```{r}
regional_domestic_tourism_individual %>% 
  mutate(nights_per_visit = nights / visits) %>% 
  group_by(local_authority) %>% 
  summarise(mean_nights_per_visit = mean(nights_per_visit, na.rm = TRUE)) %>%
  ggplot() +
  geom_col(aes(x = reorder(local_authority, mean_nights_per_visit), y = mean_nights_per_visit,
               fill = local_authority %in% c("Shetland Islands", "Orkney Islands", "Na h-Eileanan Siar",
                                             "City of Edinburgh", "Glasgow City", "Highland")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey80",
                               "TRUE" = colour_scheme[1])) +
  coord_flip() +
  labs(
    x = "Region",
    y = "Avg. Nights per Visit",
    title = "Domestic Tourism Avg. Nights per Visit") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "blank"))
```

##### Map

```{r}
regional_data_joined %>%
  mutate(nights_per_visit = nights / visits) %>% 
  group_by(local_authority) %>% 
  summarise(mean_nights_per_visit = mean(nights_per_visit, na.rm = TRUE)) %>%
  ggplot(aes(fill = mean_nights_per_visit)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Domestic Tourism Mean Nights per Visit",
    fill = "Mean Nights per Visit"
  ) +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(size = 15, face = "bold"))
  
```

#### Gross Value Added

```{r}
tourism_businesses %>%
  filter(local_authority != "Scotland",
         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
  group_by(local_authority) %>% 
  summarise(total_gva = sum(gva)) %>% 
  slice_max(total_gva, n = 5)
  
tourism_businesses %>%
  filter(local_authority %in% c("City of Edinburgh", "Glasgow City", "Aberdeen City",
                                "Highland", "Fife"),
         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
  ggplot() +
  geom_boxplot(aes(x = gva, y = local_authority, fill = local_authority), 
               alpha = 0.8,
               show.legend = FALSE) +
  scale_fill_manual(values = colour_scheme) +
  scale_colour_manual(values = colour_scheme) +
  labs(
    x = "Gross Value Added (Million GBP)",
    y = "Local Authority",
    title = "Distribution of Annual Gross Value Added",
    subtitle = "Top 5 Regions: 2009-2019"
  ) +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", 
                                  linetype = "dashed"))
```

#### Scottish Based Tourism Compared To English Based Tourism

```{r}
regional_data_joined_sco_eng %>% 
  filter(region_of_residence == "Scotland") %>%
  group_by(local_authority) %>%
  summarise(mean_visits = mean(visits)) %>% 
  ggplot(aes(fill = mean_visits)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Number of Scottish Based Vistors",
    subtitle = "By Region",
    fill = "Visits (Thousands)") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

```{r}
regional_data_joined_sco_eng %>% 
  filter(region_of_residence == "England") %>% 
  group_by(local_authority) %>%
  summarise(mean_visits = mean(visits)) %>% 
  ggplot(aes(fill = mean_visits)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Number of English Based Vistors",
    subtitle = "By Region",
    fill = "Visits (Thousands)") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

#### Marketing Edinburgh to Domestic Tourists: Mini Case Study

##### Visits by Country of Residence

```{r}
regional_domestic_tourism_non_gb_clean %>%
  filter(local_authority %in% c("City of Edinburgh")) %>% 
  ggplot(aes(x = visits, y = region_of_residence, fill = region_of_residence == "Scotland")) +
  geom_density_ridges(show.legend = FALSE, alpha = 0.5) +
  theme_ridges() +
  theme(axis.title.y = element_blank()) +
  scale_fill_manual(values = c("FALSE" = colour_scheme[2],
                               "TRUE" = colour_scheme[1])) +
  labs(
    title = "Distribution of Annual Visits by Country of Residence",
    subtitle = "Edinburgh",
    x = "Visits (Thousands)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 13),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "dashed"),
        axis.text.y = element_text(face = "bold"))
```

##### Spend Per Visit by Country of Residence

```{r}
regional_domestic_tourism_non_gb_clean %>%
  filter(local_authority %in% c("City of Edinburgh")) %>%
  mutate(exp_per_visit = expenditure / visits) %>% 
  ggplot(aes(x = exp_per_visit, y = region_of_residence, fill = region_of_residence == "Scotland")) +
  geom_density_ridges(show.legend = FALSE, alpha = 0.5) +
  theme_ridges() +
  theme(axis.title.y = element_blank()) +
  scale_fill_manual(values = c("FALSE" = colour_scheme[2],
                               "TRUE" = colour_scheme[1])) +
  labs(
    title = "Distribution of Expenditure per Visit by Country of Residence",
    subtitle = "Edinburgh",
    x = "Expenditure per Visit (Million GBP / Thousand Visits)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 13),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "dashed"),
        axis.text.y = element_text(face = "bold"))
```

##### Nights by Country of Residence

```{r}
regional_domestic_tourism_non_gb_clean %>%
  filter(local_authority %in% c("City of Edinburgh")) %>% 
  mutate(nights_per_visit = nights / visits) %>%
  ggplot(aes(x = nights_per_visit, y = region_of_residence, fill = region_of_residence == "Scotland")) +
  geom_density_ridges(show.legend = FALSE, alpha = 0.5) +
  theme_ridges() +
  theme(axis.title.y = element_blank()) +
  scale_fill_manual(values = c("FALSE" = colour_scheme[2],
                               "TRUE" = colour_scheme[1])) +
  labs(
    title = "Distribution of Nights by Country of Residence",
    subtitle = "Edinburgh",
    x = "Nights") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 13),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "dashed"),
        axis.text.y = element_text(face = "bold"))
```


##### Linear Model: Predict Spend by Visits & Nights?


```{r}
regional_domestic_tourism_non_gb_clean %>% 
  filter(local_authority == "City of Edinburgh",
         region_of_residence == "England") %>% 
  summarise(cor(expenditure, visits))
```

```{r}
regional_domestic_tourism_non_gb_clean %>% 
  filter(local_authority == "City of Edinburgh",
         region_of_residence == "England") %>% 
  summarise(cor(expenditure, nights))
```

```{r}
edinburgh_england <- regional_domestic_tourism_non_gb_clean %>% 
  filter(local_authority == "City of Edinburgh",
         region_of_residence == "England")
```


```{r}
model_edinburgh <- lm(formula = expenditure ~ visits, data = edinburgh_england)
summary(model_edinburgh)
```

```{r}
edinburgh_england %>%
  add_predictions(model_edinburgh) %>%
  add_residuals(model_edinburgh) %>% 
  ggplot(aes(x = visits, y = expenditure)) +
  geom_point() +
  geom_line(aes(y = pred), col = colour_scheme[3], size = 1) +
  labs(
    x = "Visits (Thousands)",
    y = "Expenditure (Million GBP)",
    title = "English Based Visitors To Edinburgh: Expenditure / Visits",
    subtitle = "Based On 3 Year Annual Averages Between 2009-2019")
```
Model: spend ~ visits

Interpretation: ~97% of the variation in expenditure can be explained by the number of visits. 

Question: The largest increase in visitor numbers is from 2009-2011 Avg. to 2010-2012 Avg. ~6%. If this percentage increase in visits was replicated in based on the most recent set of figures resulting in ~1803 (Thousand) visitors - what would the model predict for expenditure?

Answer: If visits were increased as above, the model would predict expenditure of ~632 Million GBP (Low Estimate ~620, High Estimate ~644)

As calculated below.

Step 1.
outcome = b0 + b1 * 1st Predictor

Step 2.
expenditure = b0(intercept) + b1(coefficient) * 1st Predictor

Step 3.
expenditure = b0(intercept) + b1(coefficient) * `visits`

Step 4.
expenditure = -493.61749 + 0.62423 * `1803`

Step 5.
expenditure = ~632 (Low Estimate ~620, High Estimate ~644)

```{r}
632 + c(-12.34, 12.34)
```

## International Tourism

### Total Visitors by Country of Residence

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_visits = sum(visits)) %>%
  slice_max(total_visits, n = 20) %>% 
  ggplot(aes(x = reorder(country, total_visits), y = total_visits)) +
  geom_col(aes(x = reorder(country, total_visits), y = total_visits,
               fill = country %in% c("USA")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = colour_scheme[1])) +
  coord_flip() +
  ylim(0, 3200) +
  labs(
    x = "Country",
    y = "Total Visits (Thousands)",
    title = "International Tourism: Total Visits (2002-2009)",
    subtitle = "Top 20 (Holiday Only)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "blank"))
```

### Total Spend by Country of Residence

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend)) %>%
  slice_max(total_spend, n = 20) %>% 
  ggplot() +
  geom_col(aes(x = reorder(country, total_spend), y = total_spend,
               fill = country %in% c("USA")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = colour_scheme[1])) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Total Spend (Million GBP)",
    title = "International Tourism: Total Spend (2002-2009)",
    subtitle = "Top 20 (Holiday Only)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "blank"))
```

### Spend per Visit by Country of Residence

#### Bar Plot

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend),
            total_visits = sum(visits),
            spend_per_visit = total_spend / total_visits) %>%
  filter(total_visits > 500) %>%
  ggplot() +
  geom_col(aes(x = reorder(country, spend_per_visit), y = spend_per_visit,
               fill = country %in% c("Australia", "China", "Canada")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = colour_scheme[1])) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Total Spend (Million GBP) / Visit (Thousands)",
    title = "International Tourism: Total Spend per Visit (2002-2009)",
    subtitle = "Countries w/ Over 500 Thousand Total Visits (Holiday Only)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "blank"))
```

#### Scatter Plot

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend),
            total_visits = sum(visits),
            spend_per_visit = total_spend / total_visits) %>%
  filter(total_visits > 500) %>% 
  ggplot(aes(x = total_visits, y = spend_per_visit)) +
  geom_point(aes(colour = country %in% c("Australia", "China", "Canada")), 
             show.legend = FALSE,
             size = 4) +
  scale_colour_manual(values = c("FALSE" = "grey60",
                                 "TRUE" = colour_scheme[3])) +
  ggrepel::geom_text_repel(aes(x = total_visits, y = spend_per_visit, label = country)) +
  labs(
    x = "Visits (Thousands)",
    y = "Total Spend (Million GBP) / Visit (Thousands)",
    title = "International Tourism: Visits vs. Spend Per Visit (2002-2009)",
    subtitle = "Countries w/ Over 500 Thousand Total Visits (Holiday Only)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "dashed"))
```

### Marketing Scotland To Canadian Based Tourists

$H_0$: $\mu_{\textrm{spend per visit(Q1+Q4)}} - \mu_{\textrm{spend per visit(Q2+Q3)}} = 0$
$H_a$: $\mu_{\textrm{spend per visit(Q1+Q4)}} - \mu_{\textrm{spend per visit(Q2+Q3)}} != 0$

```{r}
international_visits %>%
  filter(country == "Canada",
         purpose == "Holiday") %>% 
  mutate(exp_per_visit = spend / visits,
         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No")) %>%  group_by(spring_summer) %>% 
  summarise(mean_visits = mean(visits),
            mean_exp = mean(spend),
            mean_exp_per_visit = mean(exp_per_visit))
```
```{r}
canada_sample <- international_visits %>%
  filter(country == "Canada",
         purpose == "Holiday") %>% 
  mutate(exp_per_visit = spend / visits,
         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No"))
```

```{r}
observed_stat <- canada_sample %>% 
  specify(exp_per_visit ~ spring_summer) %>%
  calculate(stat = "diff in means", order = c("Yes", "No"))

observed_stat
```

```{r}
null_distribution <- canada_sample %>% 
  specify(response = exp_per_visit, explanatory = spring_summer) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("Yes", "No"))
```

```{r}
null_distribution %>%
  visualise() +
  shade_p_value(obs_stat = observed_stat, direction = "both")
```

```{r}
null_distribution %>%
  get_p_value(obs_stat = observed_stat, direction = "both")
```

